HR Dept.\\

Dear Recruiter Person,

I am aiming to a role in Product, preferably as Product Manager. I am
mostly searching through individual companies and. NGOs on a google
search basis by personal interests criteria, outside of active hiring
positions. The idea is to get ahead of what is needed at really aim for
a role that is attractive from both sides, hiring and hired.

You likely want someone that is engaged with the company's industry,
delivers solid timely results, and has experience in product. I have
been working async and remotely with global teams for over 2 years in
the tech industry, I have grown from technical positions to more
hands-on roles, with direct contact with developers and fluid
conversations with other stakeholders, such as CEOs, users, and clients.
I have a background as a sociologist: I enjoy conducting interviews,
listening to what key people can deliver as feedback, and request and
build the best features to result in the best end result on User
Experience. In my last job, as a Project Manager, I was able to be the
1st out of a group of 4 in training to achieve several milestones: work
directly with client and develepor team in CRM implementation, being in
charge of building a new product for the internal talent team of our
company, and reboot the User Interface for our internal email platform.

I hope the profile I am offering matches your needs. I understand that a
meeting may be mutually beneficial. My email to manage meetings is
benjaminjuarezarlt@gmail.com. I am available on Wednesday to Friday
morning, from 9 to 10 AM, New York Time. Would you like to meetup
sometime this week or next?

Thank you for taking the time to consider my credentials.\\
Sincerely yours,\\
~\\
~\\
Benjamin Juarez
