% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section*{Benji's career plan}


\hypertarget{year-1-strengthening-core-skills-and-network}{%
\subsubsection*{\texorpdfstring{\textbf{Year 1: Strengthening Core Skills}}{Year 1: Strengthening Core Skills and Network}}\label{year-1-strengthening-core-skills-and-network}}

\begin{itemize}
\tightlist
\item
  \textbf{Goal}: Deepen expertise in blockchain and product management
  within the social impact space.

  \begin{itemize}
  \tightlist
  \item
    \textbf{Q1/Q2}: Take certifications @scrum.org:
    Scrum Master,
    Product Owner
%     (e.g., Certified Blockchain
%     Professional or a PM certification).
  \item
    \textbf{Q2/Q3}: Attend and actively participate in at least one major
    industry conference or event related to crypto or social impact,
    such as Consensus or TechCrunch Disrupt.
  \item
    \textbf{Q3/Q4}: Continue a personal project from 2023 or contribute to an
    open-source project in the social impact space, focusing on using
    blockchain for good.
  \item
    \textbf{Q4}: Build and nurture relationships with key players in the
    social impact and blockchain communities through networking events,
    LinkedIn, and other platforms.
  \end{itemize}
\end{itemize}

\hypertarget{year-2-expanding-influence-and-impact}{%
\subsubsection*{\texorpdfstring{\textbf{Year 2: Expanding Influence and
Impact}}{Year 2: Expanding Influence and Impact}}\label{year-2-expanding-influence-and-impact}}

\begin{itemize}
\tightlist
\item
  \textbf{Goal}: Increase visibility and thought leadership within the
  industry.

  \begin{itemize}
  \tightlist
%   \item
%     \textbf{Q1}: Write and publish 2-3 articles on Medium or LinkedIn about blockchain's role in social impact, sharing insights from your projects and experience.
  \item
    \textbf{Q1/Q2}: Mentor a junior product manager or blockchain
    enthusiast, offering guidance based on your experience in crypto and
    pre-seed incubation.
  \item
    \textbf{Q2/Q3}: Lead or co-lead a workshop or webinar on blockchain and
    social impact at a conference or community event.
  \item
    \textbf{Q4}: Explore opportunities for collaboration with NGOs or
    social enterprises, potentially advising or consulting on blockchain
    solutions.
  \end{itemize}
\end{itemize}

\hypertarget{year-3-transitioning-to-leadership-roles}{%
\subsubsection*{\texorpdfstring{\textbf{Year 3: Transitioning to
Leadership
Roles}}{Year 3: Transitioning to Leadership Roles}}\label{year-3-transitioning-to-leadership-roles}}

\begin{itemize}
\tightlist
\item
  \textbf{Goal}: Move into a senior product management role or begin
  exploring entrepreneurial opportunities.

  \begin{itemize}
  \tightlist
%   \item
%     \textbf{Q1}: Apply for senior product management roles with a focus
%     on blockchain and social impact within innovative companies or
%     startups.
  \item \textbf{Q1}: Spearhead a project that leverages blockchain for social good, such as developing a new product or improving an existing one.
  \item \textbf{Q2/Q3}: Consider starting your own venture or joining an early-stage startup as a co-founder or key team member, focusing on blockchain solutions for social impact.
  \item
    \textbf{Q4}: Continue to build your public profile through speaking
    engagements, panel discussions, or being featured in industry
    podcasts.
  \end{itemize}
\end{itemize}

\bigskip

\hypertarget{year-4-5-establishing-authority-and-broadening-horizons}{%
\subsubsection*{\texorpdfstring{\textbf{Years 5-10: Establishing Authority
and Broadening
Horizons}}{Years 5-10: Establishing Authority and Broadening Horizons}}\label{year-4-5-establishing-authority-and-broadening-horizons}}

\begin{itemize}
\tightlist
\item
  \textbf{Goal}: Solidify your position as a thought leader and
  potentially transition to a founder or executive role.

  \begin{itemize}
  \tightlist
  \item
    \textbf{Year 5}:

    \begin{itemize}
    \tightlist
    \item
      Scale your impact by leading a major product or initiative that
      achieves significant social outcomes using blockchain.
    \item
      If entrepreneurial, secure funding for your startup and lead it
      through a successful launch.
    \end{itemize}
  \item
    \textbf{Year 10}:

    \begin{itemize}
    \tightlist
    \item
      Become a recognized authority in the intersection of blockchain,
      product management, and social impact, with regular invitations to
      speak at top-tier conferences.
    \item
      Consider publishing a book or extensive guide on blockchain for
      social good.
    \item
      If your startup has gained traction, consider expansion or
      exploring new markets.
    \end{itemize}
  \end{itemize}
\end{itemize}

% This plan is designed to build on Benji's existing strengths while
% expanding their influence and leadership in the industry. It also allows
% for flexibility in either deepening expertise within organizations or
% pursuing entrepreneurial ventures.

% \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
