%\chapterstyle{default} % Reset the chapter style back to the default used for non-content chapters

%\end{document} 

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------



\section*{Videography}


\bibitem{} BENNA J.B. 2008v. \textit{Ultramarathon Man: 50 Marathons, 50 States, 50 Days}. Journeyfilm.
109 min.

\bibitem{} Charitywater. 2011v. \textit{Water changes everything}. youtube. 4 mins.

\bibitem{} Charity: water. 2012v. \textit{Rachel Beckwith’s Mom Visits Ethiopia}. vimeo. 5 mins.

\bibitem{} COEMAN, Tom. 2012v. \textit{Marathonman 365}. Bull’s eye films. 52 min.

\bibitem{} DREYER, Danny. 2004v. \textit{ChiRunning DVD: A Revolutionary Approach to Effortless, Injury-free Running}. 64 mins.

\bibitem{} DUNHAM, Jon. 2007v. \textit{Spirit of the Marathon}. Calico 1880. 104 min.

\bibitem{} EHRLICH, Judd. 2008v. \textit{Run for Your Life (I)}. Flatbush Pictures.

\bibitem{} End Slavery Now. 2014v. \textit{End Slavery Now Website Relaunch}. vimeo. 3 mins.
Epipheo. 2010v. Do you own (stuff made by) slaves? youtube. 2 mins.

\bibitem{} FRANKEL, Davey Frankel & LAKEW, Rasselas. 2009v. \textit{Atletu}. AV Patchbay. 92 min.

\bibitem{} HEISENBERG, Benjamin. 2010v. \textit{Der Räuber}. Nikolaus Geyrhalter Filmproduktion. 101 min.

\bibitem{} MIERKE, Ken. 2005v. \textit{Evolution running: run faster with fewer injuries}. Endurance Films. 46 min.

\bibitem{} MOLL, James. 2007v. \textit{Running the Sahara}. Allentown Productions. 102 min.

\bibitem{} RICHARDSON, Tony. 1962v. \textit{The Loneliness of the Long Distance Runner}. Woodfall
Film Productions. 104 min.

\bibitem{} ROMANOV, Dr. Nicholas. 2001v. \textit{Pose Method of Running}. Train with the Czar. 60 mins.

\bibitem{} ROTHWELL, Jerry. 2012v. \textit{Town of Runners}. Met Film Production. 80 min.

\bibitem{} STEWART, Rob. 2006v. \textit{Sharkwater}. SW Productions. 89 min.

\bibitem{} STRETANSKI, David. 2010v. \textit{ChiRunning Simplified!, Efficient and Injury Free Natural Running Form Technique Video} youtube (echifitness). 10 mins.

\bibitem{} STUART, Mel. 2000v. \textit{Running on the Sun: The Badwater 135}. Galaxy Entertainment.
100 min.
