\section*{Strengths \& Weaknesses}

My Strengths are based on my Gallup Strengths:
\begin{description}
 \item [Believer]
 \item [Philomath]
 \item [Coach]
 \item [Self-Believer]
 \item [Strategist]
\end{description}

% \noindent
% My areas to improve come from Personality overall.

\subsection*{Strengths}

\begin{description}
 \item[Belief] in: people's capabilities and that they can bring a lot to the table, from both a work and personal view.
 self, others, team, company.
 My view %of the company and team
 makes me %super
 high drive, and persistent.
\item[Curious.] I love learning, but my fuel is in placing questions forward and not staying stagnant with a simple eternal answer. Iteration and nuance are key.
\item[Supportive.] I push causes to happen, and I believe we can all give something out to the world. wagmi: we're all gonna make it.
\item[Ownership.] I believe to have both confidence and certainty to move forward, and I strive for other people to gain them as well.
\item[Strategist.] Always aiming for the big picture: am I going to be happy about this work in 20 to 50/200 years? I hope so. Let's plan steps and execute!
 \end{description}

\subsection*{Weaknesses}

\noindent
My areas to improve come from Personality overall:
INTJ
+
Type 5 / Wing 4

\begin{description}
 \item[Contrarian:] sometimes wrongly, :P
 \item[] \> \> \>
%  \hrule
%  $ $ $ $
 I believe in people's intent and their heart-felt beliefs and actions. At the same time,
 I can disagree with their ideas and perspectives,
 and it's a challenge to communicate both angles.
%  at the same time
 \item[Interruptor:] a fine art that ought never be learned :P \\
 I get excited about a conversation and want to contribute. Video calls do help with this:
 because you have to unmute, and really
 check if the other person is OK and wrapped their idea.
%  pay attention to pauses in conversation before speaking.
 \item[Overly Imaginative:] going off rail to derivatives can be unproductive for working on immediate goals. Let's better plan one step at a time %so we can
 to stay in sync
 \item[Data insufficient:] I'm biased to teamwork and intuition. It's OK to build quickly and iterate, but %it would  be
 it's best to plan strategies with hard-data. % based decisions.
 It's one of my next steps, but not there yet.
%  \item[Unexperienced Professional Background:] no well-known, big-name company on my resume as an employer. Primary experience in unstructured companies, mostly regional, in LatinAmerica, and in a promising Music Startup (with HQ in US and Europe) but that hasn't yet gained traction.
%  \item[]
\item[Stakeholder Influence.] Even though I feel in general to have good relationships across teams, I may need to review what my leverage is, and how much I can or should influence across company.
 \end{description}
